AA Distributed Software Development Methodology

### 2012-04-17 paper.tex
AA Methodology - Session
Added an overlook of how an aa session works and why, probably good expand it,
also added the link for agile manifesto for referencing later

\section{Related Work}
\todo{survey other methodologies such as agile etc}

@@

>>>>

\section{Related Work}
\todo{survey other methodologies such as agile etc}
\todo{probably a good source http://agilemanifesto.org/}

@@

\section{AA Session}

From the developer perspective, the AA methodology is based on creating pretty
small high perspective reports of what they're doing in a specific timeframe,
that can be something between 5 to 15 minutes, depending in what is more
confortable for the developer, an AA Session would be a period of at least 2hrs
doing these reports. The developer can set reminders to show up when its time
to make a new report.

The objective of the flexible timeframe and reminders is to don't generate much
overhead for the developer to be in an AA session, so he can make the reports
and also concentrate in his code.

Each report can be sent directly to the an online server, or cached locally in
a log for sending later, this is necessary to make possible for developers that are
offline to use AA without problems.

The developer can also add a screencast in the end of session to make a summary
of what has been done in the session, explaining with his words and showing his
results, possibly making some points more easily understandable then with only
the reports from the AA session.
